---
title: "Applying Statistics to Kickstarter Data"
output: pdf_document
---

```{r include=TRUE}
# libraries
library(tidyr)
library(anytime)
library(readr)
library(lubridate)
library(ggplot2)

# data
#import csv file
ks <- read_csv("~/Downloads/train.csv")

# Get the data set ready  
# 1. only include US $ currency 
ks_us <- subset(ks, currency == "USD")

#2. change date unix format:
ks_us$deadline <- anytime(ks_us$deadline)
ks_us$created_at <- anytime(ks_us$created_at)
ks_us$launched_at <- anytime(ks_us$launched_at)
ks_us$state_changed_at <-anytime(ks_us$state_changed_at)


# extract dealine hour
ks_us$deadline_hour <- hour(ks_us$deadline)

#extract year, month and day
ks_us$deadline <- as.Date(strptime(ks_us$deadline, "%Y-%m-%d"))
ks_us$created_at <- as.Date(strptime(ks_us$created_at, "%Y-%m-%d"))
ks_us$launched_at <- as.Date(strptime(ks_us$launched_at, "%Y-%m-%d"))
ks_us$state_changed_at <- as.Date(strptime(ks_us$state_changed_at, "%Y-%m-%d"))


#days between created and deadline
ks_us$date_cd <- difftime(ks_us$deadline,ks_us$created_at, units = "days")
ks_us$date_cd <- as.numeric(ks_us$date_cd)

#add day of the week for deadline
ks_us$deadlineday <- weekdays(as.Date(ks_us$deadline))

# turn final status from numeric into a factor
ks_us$final_status = as.factor(ks_us$final_status)

# Change 0/1 to unfunded and funded
ks_us$final_status <- factor(ks_us$final_status, levels=c(0,1), labels=c("unfunded", "funded"))


```

Apply Statistics to the Data
```{r}
# Can you count something interesting?
# 1. How many projects get funded? #30573
sum(ks_us$final_status == "funded")


# Amount of days related to funding status
days365 <- ks_us[ which(ks_us$date_cd < 365), ]
ggplot(days365, aes(final_status, date_cd)) + geom_boxplot()


# distribution of how many days the projects were active
ggplot(ks_us, aes(date_cd)) + geom_histogram(binwidth = 5, aes(colour=final_status))
ggplot(days365, aes(date_cd)) + geom_histogram(binwidth = 5, aes(colour=final_status))

summary(ks_us$date_cd[ks_us$final_status=="funded"])
summary(ks_us$date_cd[ks_us$final_status=="unfunded"])

# goal amount ?? better visuals ??
ggplot(ks_us, aes(goal)) + geom_area(stat = "bin", aes(colour=final_status))

ggplot(ks_us, aes(goal)) + geom_histogram(binwidth = 100, aes(colour=final_status))



# goal amount vs project length
ggplot(ks_us, aes(date_cd, goal)) + geom_jitter(aes(colour = final_status))
ggplot(days365, aes(date_cd, goal)) + geom_jitter(aes(colour = final_status))

#goal amount vs backers
ggplot(ks_us, aes(backers_count, goal)) + geom_jitter(aes(colour = final_status))

goal1k <- ks_us[ which(ks_us$goal<1000), ]
ggplot(goal1k, aes(backers_count, goal)) + geom_jitter(aes(colour = final_status))

summary(ks_us$goal[ks_us$final_status=="funded"])
summary(ks_us$goal[ks_us$final_status=="unfunded"])


# goal to deadline hour
ggplot(ks_us, aes(deadline_hour, goal)) + geom_bar(stat="identity", aes(colour = final_status))
ggplot(goal1k, aes(deadline_hour, goal)) + geom_bar(stat="identity", aes(colour = final_status))


# deadline hour distribution
ggplot(ks_us, aes(deadline_hour)) + geom_histogram(binwidth = 1, aes(colour=final_status))

summary(ks_us$deadline_hour[ks_us$final_status=="funded"])
summary(ks_us$deadline_hour[ks_us$final_status=="unfunded"])


# day of the week vs funding
# how put in order of day? 
deadlineday <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")

ggplot(ks_us, aes(deadlineday, goal)) + geom_bar(stat = "identity", aes(colour = final_status)) + scale_x_discrete(limits = deadlineday)



```  

## Initial Observations of the Data
Total Kickstarter projects is 10,8129. For this analysis we are only focusing on projects with US dollars used, which is 85% (92,033). Of these projects, 33% (30,573) get fully funded. 

## Trends
### Project Length
There is a wide range of how many days a project is active. Both funded and unfunded have a range from a day or two to over four years. The median for both is close. Median for unfunded is 48 and median for funded is 49.  

### Goal Amount
Obvious observation is the more backers per goal, the higher chance the project had at succeeding. 
The unfunded projects. The Median goal amount for funded projects is $3,500 and the mean is $9,881. 

### Deadline Hour
The deadline hours for both funded and funded follow the same trend. Earlier in the morning and later at night are more popular times versus 8pm - 12am being the the least likely for a project to end. 

### Deadline Day
Nothing surprising with the deadline day. Both funded/unfunded have more deadline days over Thursday to Saturday. Sunday to Wednesday is fairly steady with the lowest on Tuesday. 

## Future Thoughts
The length of time a project is active could lead to further insights. We'll look into this further to see if there is anything to pull from the shorter or longer active project lengths. 




