---
title: "Turning your Kickstarter idea into a reality"
---

## Intro: Why do some Kickstarter ideas get funded and others do not?   

### Why Kickstarter?
Kickstarer's mission is to help bring creative projects to life. Since launching in 2009, 14 million people have backed a project, $3.4 billion has been pledged, and 134,135 projects have been successfully funded. Projects have many forms including food and publishing to music, fashion and technology. 

Kickstarter is all or nothing. If a project doesn't get every dollar, the project will not be succesful. We are going to dive into what makes a project succesful or not.      

### Data  
To predict whether a project will get funded or not, we will look at the (Kaggle data set). https://www.kaggle.com/codename007/funding-successful-projects 
The data contains ... variables (do I need to explain them or just a few?). 

## Working with the Data

Libraries
```{r}
library(dplyr)
library(tidyr)
library(anytime)
library(readr)
library(lubridate)
library(ggplot2)
```

Import and clean up the data
Because the data is from a Kaggle competition, it is fairly clean. There are no missing variables.
```{r}
#import csv file
ks <- read_csv("~/Downloads/train.csv")
View(ks)

# Get the data set ready  
# 1. only include US $ currency 
ks_us <- subset(ks, currency == "USD")

#2. change date unix format:
ks_us$deadline <- anytime(ks_us$deadline)
ks_us$created_at <- anytime(ks_us$created_at)
ks_us$launched_at <- anytime(ks_us$launched_at)

# extract dealine hour
ks_us$deadline_hour <- hour(ks_us$deadline)

#extract year, month and day
ks_us$deadline <- as.Date(strptime(ks_us$deadline, "%Y-%m-%d"))
ks_us$created_at <- as.Date(strptime(ks_us$created_at, "%Y-%m-%d"))
ks_us$launched_at <- as.Date(strptime(ks_us$launched_at, "%Y-%m-%d"))

#days between created and deadline
ks_us$date_cd <- difftime(ks_us$deadline,ks_us$created_at, units = "days")

#add day of the week for deadline
ks_us$deadlineday <- weekdays(as.Date(ks_us$deadline))


```

## Exploratory Analysis
Now that we have our metrics determined, we will start digging into what the data has to tell us. We are working with 92,0333 projects from April 2009 - May 2015. 
```{r}
# explore funded data
sum(ks_us$final_status)

# total funded = 30573 (33.2%)
ks_funded <- ks_us[ks_us$final_status=="1",]
mean(ks_funded$goal) #9880.844

plot(ks_funded$goal) 


# explore unfunded
ks_unfunded <- ks_us[ks_us$final_status=="0",]
mean(ks_unfunded$goal) #43599.01

plot(ks_unfunded$goal)

#box-plots
ks_us$final_status <- as.factor(ks_us$final_status)

# plot goal both funded & unfunded
boxplot(goal~final_status, data = ks_us, outline = FALSE)

# plot backers count
boxplot(backers_count~final_status, data = ks_us, outline = FALSE)


# outliers
plot(ks_us$goal) 

plot(ks_us$backers_count) 

plot(ks_us$date_cd) 
``` 

# DELETE - playing around with the variables
Plots by variables
```{r}
# 1. Goal Amount
# scatter plot with two colors with funded vs unfunded
# plot funded vs unfunded goal on scatter plot
ggplot() + geom_point(aes(x=ks_funded$goal, y=ks_unfunded$goal))

# 2. Disable Communication
# ??? not working ???
overall how many disable communication??

false = ks_us$disable_communication)
plot(ks_us[,c("final_status","disable_communication")], main = "Box-plot of backers", outline = FALSE)

# 3. Deadline
# create distribution for both hour and day of the week
# ??? day instead of a number? 
qplot(ks_us$deadlineday, "days", geom = "histogram")
plot(ks_us$deadline_hour, )

hist(ks_us$deadlineday, "days", freq = TRUE)

# 4. How many days between start and deadline
boxplot(date_cd~final_status, data = ks_us, outline = FALSE)


# 5. created

```


## Feature Engineering?



## Probability? Stats? 
logistic regression / cart & random forest


## Findings 



## Recommendations




