---
title: "Kickstarter: Data Wrangling"
output: html_notebook
---
```{r}

```

Packages Used

```{r}
library(dplyr)  
library(tidyr)  
library(anytime)  
library(readr)  
library(lubridate)  
```

Import & View the data
```{r}
ks <- read_csv("~/Downloads/train.csv.zip")
View(ks)
```


Clean up the data 
1. Only include US $ currency  
```{r}
ks_us <- subset(ks, currency == "USD")
```

2. Change date unix format 
```{r}
ks_us$deadline <- anytime(ks_us$deadline)
ks_us$created_at <- anytime(ks_us$created_at)
ks_us$launched_at <- anytime(ks_us$launched_at)
```

3. Extract dealine hour
```{r}
ks_us$deadline_hour <- hour(ks_us$deadline)
```

4. Extract year, month and day
```{r}
ks_us$deadline <- as.Date(strptime(ks_us$deadline, "%Y-%m-%d"))
ks_us$created_at <- as.Date(strptime(ks_us$created_at, "%Y-%m-%d"))
ks_us$launched_at <- as.Date(strptime(ks_us$launched_at, "%Y-%m-%d"))
```


Create New Metrics
Days between created and deadline
```{r}
ks_us$date_cd <- difftime(ks_us$deadline,ks_us$created_at, units = "days")
```


Do we need disabled communication?
Look for True
delete column if not adding any value to analysis

```{r}

???


```




Getting to know the data
1. explore funded data
```{r}
ks_funded <- ks_us[ks_us$final_status=="1",]

mean(ks_funded$goal)

ks_funded[ks_funded$goal>1000,]


```

Funded Info
-mean $9,881



Explore unfunded

```{r}

ks_unfunded <- ks_us[ks_us$final_status=="0",]

mean(ks_unfunded$goal)

```

Box-Plots
```{r}
ks_us$final_status <- as.factor(ks_us$final_status)

# plot goal
plot(ks_us[,c("final_status","goal")], main = "Box-plot of goal", outline = FALSE)

# plot backers count
plot(ks_us[,c("final_status","backers_count")], main = "Box-plot of backers", outline = FALSE)

```





Outliers
```{r}
plot(ks_us$goal) 

plot(ks_us$backers_count) 

plot(ks_us$date_cd) 
```


Exploring Deadline Hour

```{r}
plot(ks_us$deadline_hour)

hist(ks_us$deadline_hour)

hist(ks_funded$deadline_hour)

hist(ks_unfunded$deadline_hour)


```




